Think again?\\ Optimal mental simulation tracks problem difficulty

### 2015-01-29 manuscript.tex
Add Kevin's edits

%% The question we're interested in: how many simulations do people take?
Imagine you are playing a video game---for example, Angry Birds or Desert Golf---in which you need to predict where an object will end up. How do you know where to aim, and how long do you spend thinking about each shot before you take it? Recent research in the domain of intuitive physics and mental simulation has revealed that people make predictions like these by running noisy physical simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}. However, while this research has investigated the \emph{mechanism} by which people make these types of predictions, there has been very little investigation into \emph{how} people actually use this mechanism. If people are running mental simulations, \emph{how many} simulations do they run?

%% What's already been done
According to previous research by \citeA{Vul:2014ba}, a sample-based agent should only take a small number of samples before making a judgment---perhaps even just one. While taking a single sample is clearly suboptimal for each individual judgment, over the long run, taking a small number of samples maximizes expected utility across a large number of judgments. Does this story also hold true for mental simulations? There is some evidence that points to ``yes'': \citeA{Battaglia2013} analyzed the variability of people's responses in tasks concerning towers of building blocks, and found that participants seemed to use between three and seven samples per judgment.

A second question concerns the actual strategy used to take samples. Do people always take exactly the same number of samples for each decision, or do they vary the number of samples based on problem difficulty? While \citeA{Vul:2014ba} looked at a variety of strategies, they concluded that regardless of strategy, the optimal solution was still roughly the same: the agent should take very few samples. However, that does not make the choice of strategy irrelevant. If the strategy tells the agent to vary the number of samples, then we should see variability in the agent's response times. Indeed, such variability can be observed in other types of decision-making tasks, and has been well-modeled by the \textit{sequential probability ratio test} \cite{wald1947sequential}, or SPRT \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}. In SPRT, the agent takes samples until it reaches a threshold number of samples in support of one hypothesis over another hypothesis.

\begin{figure*}[t]
    \begin{center}
        \includegraphics[width=\textwidth]{figures/experiment.png}
        \caption{\textbf{Example experimental trial.} Each panel shows a different part of the trial. The left panel shows the initial screen presented to the participant. The middle panel shows the occluded ball, after observing the stimulus presentation. The faded gray line shows the path the ball took during the initial presentation. The right panel shows the final position of the ball, after observing the feedback. As in the middle panel, the faded gray line shows the path of the ball.}
        \label{fig:experiment}
    \end{center}
\end{figure*}

%% What we're going to do and how we're going to do it
In this paper, we investigate the number of simulations that people run when reasoning about a task that requires mental simulation of physics. Specifically, we ask the question: do people vary the number of mental simulations that they run depending on the difficulty of the problem? And, if so, do they do so in a manner consistent with SPRT? To answer these questions, we ran a behavioral experiment in which people watched a ball bouncing around in a box, and had to judge whether it would first go through a hole in the wall, or bounce off that wall. We varied the difficulty of each trial by changing the size of the holes and the margin by which the ball either went through the hole or missed the hole. We hypothesized that people should be faster to respond on ``easy'' trials (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole), and slower to respond on ``hard'' trials (e.g., where the ball just barely goes through the hole, or just barely misses the hole). In brief, find that people's responses are well-predicted by a model of simulation, and that their response times are well-predicted by combining that model with a SPRT strategy.

%% Plan of the paper
The plan of the paper is as follows. First, we describe an experiment in which we asked participants to respond to the question of, ``will the ball go through the hole?'', and analyze people's accuracy and response times. Second, we formalize our hypothesis of how people make judgments in this experiment by specifying a combination of a simulation-based model with the SPRT strategy. Third, we describe a second experiment based on the experiment from \citeA{Smith:2013fc} that was used to fit the parameters of our model. Then, we compare the model's predictions to people's responses in Experiment 1. Finally, we discuss the implications of our results on the broader, underlying question: how do people use mental simulation?

\section{Experiment 1: Will the ball go in the hole?}

\begin{figure*}[t]
    \begin{center}
        \includegraphics[width=\textwidth]{figures/hole_empirical_results.pdf}
        \caption{\textbf{Response times as a function of response.} Left subplot: each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color). Middle subplot: like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times. Right subplot: each point corresponds to a different stimulus, feedback type, and hole size.  The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.}
        \label{fig:pct-vs-rt}
    \end{center}
\end{figure*}

In order to determine whether people take multiples samples---and if they vary the number of samples---we designed an experiment in which people had to determine whether a ball would go into a hole (see Figure \ref{fig:experiment}). In particular, we designed the trials in this experiment such that some were harder than others.

@@

The experiment was divided into two phases: the training phase, and the experimental phase. During the training phase, participants made judgments on the seven instruction trials in order to get used to the task. During the experimental phase, participants made judgements on the 48 experimental trials, presented in a random order, as well as the eight control trials, which were also shown in a random order, but interspersed with the experimental trials such that every 8th trial was a control trial.

On each trial, participants were shown the scene, including the initial position of the ball and the location of the hole. Participants were instructed to press the ``space'' key to begin the trial. Immediately upon pressing ``space'', the initial stimulus presentation began. As soon as the initial stimulus animation concluded, a gray box was drawn over the screen, occluding the ball (but not the line depicting the path it had traveled so far; this was left in as a reminder to participants of where the ball had come from). Participants were asked, ``will the ball go in the hole?'', and were instructed to press `q' to respond in the affirmative, and `p' to respond in the negative. Immediately after responding, text appeared saying ``Correct!'' or ``Incorrect.'', depending on the participants' response. Additionally, the gray occluder was removed, and participants were shown the feedback animation. After the feedback animation was complete, the final frame of the animation remained on the screen until participants pressed ``space'' to advance to the next trial.

@@

As shown in Figure \ref{fig:pct-vs-rt} (right subplot), we found a clear effect of certainty on people's response times. In particular, participants were on average faster to respond on trials that they were more certain about, and slower to respond to trials that they were unsure about. This tradeoff mirrors the same tradeoff found in SPRT: decisions for which $p\approx0.5$ are slower, because it takes longer to get to one threshold versus the other. Thus, it is clear that people are not spending a fixed amount of time thinking about each trial; rather, they spend more time thinking about the ``hard'' trials than the ``easy'' trials.

\section{Modeling mental simulations}

How do people make the types of judgments that they did in Experiment 1? We hypothesized that they predict where the ball will go by running noisy physical simulations, and that they run a variable number of simulations on each trial according to the \textit{sequential probability ratio test}, or SPRT \cite{wald1947sequential}. In this section, we lay out the formalism for both the simulation-based model and the SPRT strategy.

\subsection{The ``Noisy Newton'' hypothesis}

There is a growing body of evidence that people reason about physical scenes by running noisy simulations. This hypothesis, referred to as the ``Noisy Newton'' hypothesis, states that people have approximate knowledge of physical laws instantiated in a runnable model of intuitive physics. Using this model, they can extrapolate the future of physical scenes by running a series of noisy simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}. In particular, \citeA{Smith:2013fc} investigated the various sources of uncertainty in these simulations, finding that people's judgments were best captured by a model that took into account both perceptual uncertainty and dynamics uncertainty.

@@

\subsection{The SPRT strategy}

In this paper, we consider binary (or two-alternative forced choice) decisions, where an agent must choose one of two hypotheses, $H_0$ or $H_1$. The agent may take samples $X_i$ from a Bernoulli distribution parameterized by an unknown parameter $p$, and from these samples estimate $\hat{p}=\frac{1}{N}\sum_{i=1}^N X_i$, where $N$ is the total number of samples. Then, the decision rule which minimizes the probability of error is $\hat{H}(X_1,\ldots{},X_N)=H_0$ when $\hat{p}<0.5$ and $\hat{H}(X_1,\ldots{},X_N)=H_1$ when $\hat{p}>0.5$.

In the best possible case, the agent takes infinite samples and chooses the maximum \emph{a posteriori} (MAP) hypothesis with probability $p$. In practice, the agent cannot take infinite samples. Thus, to determine when to stop sampling (i.e., what the value of $N$ is), we use the \emph{sequential probability ratio test} \cite{wald1947sequential}. When using a SPRT strategy, the agent accumulates $Y_N=\sum_{i=1}^N 2X_i-1$, and stops either when $Y_N=T$ or $Y_N=-T$, for some threshold number of samples $T$.

\subsubsection{Modeling responses} Independent of the number of samples actually taken, the probability of choosing $H_1$ given that $H_1$ is the MAP hypothesis is:
\begin{equation}
\Pr[\hat{H}(Y_N)=H_1\,|\,H_1]=\frac{p^T}{p^T+(1-p)^T},
\label{eq:pr-choose-h1}
\end{equation}

We can compute the probability, $p$, that the ball goes in the hole by running simulations from the model.

\subsubsection{Modeling response times} Given the threshold, the probability of taking $N$ samples and then choosing $H_1$ is:
\begin{multline}
\Pr[N,H_1\,|\,T,p]=\left(\frac{2^N}{2T}\right)p^{\frac{N+T}{2}}(1-p)^{\frac{N-T}{2}}\cdot{}\\
\sum_{\nu=1}^{2T-1}\cos\left(\frac{\nu\pi}{2T}\right)^{N-1}\sin\left(\frac{\nu\pi}{2T}\right)\sin\left(\frac{\nu\pi}{2}\right)
\end{multline}
for $N\geq T$ and where $N$ is of the same parity as $T$ \cite[ch.~XIV, eq. 5.7]{Feller:1968ut}. Because we are dealing with binary hypotheses, the marginal probability of $N$ samples is then:
\begin{equation}
\Pr[N\,|\,T,p]=\Pr[N,H_1\,|\,T,p]+\Pr[N,H_1\,|\,T,1-p].
\label{eq:pr-n}
\end{equation}
and so the expected number of samples for a particular decision is:
\begin{equation}
\mathbb{E}[N\,|\,T,p]=\sum_{N=T}^\infty N\cdot{}\Pr[N\,|\,T,p]
\end{equation}

Assuming every sample takes the same amount of time, response times as predicted by the model should be directly proportional to $\mathbb{E}[N\,|\,T,p]$. However, we found the number of bounces to be an extremely strong predictor of response time in Experiment 1: each additional bounce adds a constant amount of time to the response. To account for this, our final response time equation incorporated the number of bounces, $B$, as follows:
\begin{equation}
t = \beta_0 + (\beta_1 + \beta_2\cdot{}\mathbb{E}[B]) \cdot{}\mathbb{E}[N\,|\,T,p]
\label{eq:rt}
\end{equation}
where $\beta_0$, $\beta_1$, and $\beta_2$ are fitted coefficients.

\section{Experiment 2}

>>>>

%% The question we're interested in: how many simulations do people take?
Imagine you are playing the game Angry Birds, where the goal is to launch a bird to knock down a tower. As you aim the bird, you need to predict where the bird will go to decide whether your shot will have the desired effect. How do you know where to aim, and how long do you spend thinking about each shot before you take it? If you shoot the bird without spending time to consider where it will go, your shot will likely be far off. But on the other hand, if you spend too long aiming, over time your predictions will only get marginally better, and you eat into the time you have to play until your next meeting. Making this physical prediction requires a tradeoff that underlies many cognitive tasks: spending time and cognitive resources to increase confidence about what will transpire next, versus using that information to make decisions in the moment. In this paper, we study whether people efficiently trade off between information seeking and exploitation in a physical prediction task.

Recent research in the domain of physical reasoning has revealed that people make predictions like these by running noisy physical simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015} - the noisy Newton hypothesis \cite{Sanborn2013}. However, while this research has investigated the \emph{mechanism} by which people make these types of predictions, there has been very little investigation into \emph{how} people actually use this mechanism. If we are running mental simulations, how to we choose how many sample simulations to run?

In this paper, we focus on a dichotomous prediction task---will a ball in motion on a computer screen go through a hole or miss it? What would be considered an `efficient' mechanism for taking samples will depend on the structure of the task, and there is a large body of literature discussing how a sample-based agent should make a decision between two choices. Specifically, we consider the \textit{sequential probability ratio test}, or SPRT\cite{wald1947sequential} strategy, in which an agent takes samples that point to one hypothesis or another, and continues to do so until the net samples in favor of one hypothesis reaches a threshold, at which point that hypothesis wins. SPRT has been used successfully to explain behavior in a number of decision-making tasks \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}, as it provides an optimal cost / benefit tradeoff between sampling and exploiting information \TODO{Can we claim this? If so, we need a citation}. While SPRT is traditionally applied to simple binary decisions (e.g., go left or go right), this framework can be extended with probabilistic physical simulations to make binary decisions about our world.

Crucially, the SPRT framework allows us to make testable predictions about how quickly people perform these dichotomous tasks. Because it involves sampling until the net evidence reaches a threshold, the number of samples will depend on the variability of the hypotheses. If samples always provide the same information, this net evidence will reach the threshold quickly, and fewer samples will be taken. On the other hand, if samples are more evenly distributed, it will take more samples to reach the net evidence threshold. Thus if people are using an SPRT strategy, we would expect that reaction times on a dichotomous task will vary systematically with task difficulty.

%% What's already been done
\TODO{MOVE THIS TO THE DISCUSSION TO EXPLAIN THE LOW THRESHOLD WE FIND: According to previous research by \citeA{Vul:2014ba}, a sample-based agent should only take a small number of samples before making a judgment so long as there is any cost to taking samples---perhaps even just one. While taking a single sample clearly provides a worse chance of making a good decision than taking multiple samples, over the long run, taking a small number of samples maximizes expected utility across a large number of judgments. Does this story also hold true for mental simulations? There is some evidence that points to ``yes'': \citeA{Battaglia2013} analyzed the variability of people's responses in tasks concerning towers of building blocks, and found that participants seemed to use between three and seven samples per judgment.}

%% What we're going to do and how we're going to do it
In this paper, we investigate whether peoples' behavior on a dichotomous physical prediction task can be explained by taking samples from a noisy Newton physical prediction model, where the number of samples taken is determined by SPRT. To answer these questions, we ran a behavioral experiment in which people watched a ball bouncing around in a box, and had to judge whether it would first go through a hole in the wall, or bounce off that wall. We varied the difficulty of each trial by changing the size of the holes and the margin by which the ball either went through the hole or missed the hole. We hypothesized that people should be faster to respond on ``easy'' trials (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole), and slower to respond on ``hard'' trials (e.g., where the ball just barely goes through the hole, or just barely misses the hole). In brief, find that people's responses are well-predicted by a model of simulation, and that their response times are well-predicted by combining that model with a SPRT strategy.

%% Plan of the paper
Here we first explain the SPRT framework and how it makes predictions about the number of samples required based on variability in sampling. Next we describe an experiment in which we asked participants to respond to the question of, ``will the ball go through the hole?'', and analyze peoples' accuracy and response times. We then demonstrate that combining the physical prediction model from \citeA{Smith:2013fc} with SPRT can explain the empirical pattern of accuracy and response times we observed. Finally, we discuss the implications of our results on the broader, underlying question: how do people use mental simulation?

\begin{figure*}[t]
    \begin{center}
        \includegraphics[width=\textwidth]{figures/experiment.png}
        \caption{\textbf{Example experimental trial.} Each panel shows a different part of the trial. \emph{Left:} the initial screen presented to the participant. \emph{Middle:}  the screen is occluded after observing the stimulus presentation. The faded gray line shows the path the ball took during the initial presentation. \emph{Right:} the final position of the ball, after observing the feedback. As in the middle panel, the faded gray line shows the path of the ball.}
        \label{fig:experiment}
    \end{center}
\end{figure*}

\section{The SPRT strategy}

In this paper, we consider binary (or two-alternative forced choice) decisions, where an agent must choose one of two hypotheses, $H_0$ or $H_1$. The agent may take samples $X_i$ from a Bernoulli distribution parameterized by an unknown parameter $p$ (the probability of sampling evidence for $H_1$), and from these samples estimate the probability that $H_1$ is correct: $\hat{p}=\frac{1}{N}\sum_{i=1}^N X_i$, where $N$ is the total number of samples. Then, the decision rule which minimizes the probability of error is $\hat{H}(X_1,\ldots{},X_N)=H_0$ when $\hat{p}<0.5$ and $\hat{H}(X_1,\ldots{},X_N)=H_1$ when $\hat{p}>0.5$.

In the best possible case, the agent takes infinite samples and chooses the maximum \emph{a posteriori} (MAP) hypothesis with probability $p$. In practice, the agent cannot take infinite samples. Thus, to determine when to stop sampling (i.e., what the value of $N$ is), the agent continues to sample until the net evidence $Y_N$ reaches some threshold, either $Y_N=T$ to select in favor of $H_1$ or $Y_N=-T$ to select in favor of $H_0$. Net evidence is the sum of samples in favor of $H_1$ minus those in favor of $H_0$, or $Y_N=\sum_{i=1}^N 2X_i-1$.

\subsection{Selecting responses} Independent of the number of samples actually taken, the probability of choosing $H_1$ given that $H_1$ is the MAP hypothesis is:
\begin{equation}
\Pr[\hat{H}(Y_N)=H_1\,|\,H_1]=\frac{p^T}{p^T+(1-p)^T},
\label{eq:pr-choose-h1}
\end{equation}

\subsection{Expected number of samples} Given the threshold $T$, the probability of taking $N$ samples and then choosing $H_1$ is:
\begin{multline}
\Pr[N,H_1\,|\,T,p]=\left(\frac{2^N}{2T}\right)p^{\frac{N+T}{2}}(1-p)^{\frac{N-T}{2}}\cdot{}\\
\sum_{\nu=1}^{2T-1}\cos\left(\frac{\nu\pi}{2T}\right)^{N-1}\sin\left(\frac{\nu\pi}{2T}\right)\sin\left(\frac{\nu\pi}{2}\right)
\end{multline}
for $N\geq T$ and where $N$ is of the same parity as $T$ \cite[ch.~XIV, eq. 5.7]{Feller:1968ut}. Because we are dealing with binary hypotheses, the marginal probability of $N$ samples is then:
\begin{equation}
\Pr[N\,|\,T,p]=\Pr[N,H_1\,|\,T,p]+\Pr[N,H_1\,|\,T,1-p].
\label{eq:pr-n}
\end{equation}
and so the expected number of samples for a particular decision is:
\begin{equation}
\mathbb{E}[N\,|\,T,p]=\sum_{N=T}^\infty N\cdot{}\Pr[N\,|\,T,p]
\label{eq:expsamp}
\end{equation}

\section{Experiment}

In order to determine whether people take physical simulation samples in a way consistent with SPRT, we designed an experiment in which people made a binary judgment about what will happen in the future---will a ball traveling through a computer screen go through a hole or not (see Figure \ref{fig:experiment})? In particular, we designed the trials such that some were harder than others. If people are using an SPRT sampling strategy, we would expect people to take longer (due to more sampling) when it was more ambiguous whether the ball would go through the hole.

@@

\begin{figure*}[t]
    \begin{center}
        \includegraphics[width=\textwidth]{figures/hole_empirical_results.pdf}
        \caption{\textbf{Response times as a function of response.} \emph{Left:} each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color). \emph{Middle:} like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times. \emph{Right:} each point corresponds to a different stimulus, feedback type, and hole size.  The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.}
        \label{fig:pct-vs-rt}
    \end{center}
\end{figure*}

@@

As shown in Figure \ref{fig:pct-vs-rt} (right subplot), we found a clear effect of certainty on people's response times. In particular, on trials when there was more agreement amongst participants (the fraction saying 'in' is closer to $0$ or $1$), participants were faster to respond than when responses were more variable. This tradeoff mirrors the same tradeoff found in SPRT: decisions for which $p\approx0.5$ are slower, because it on average takes more samples to get to one threshold versus the other. Thus, it is clear that people are not spending a fixed amount of time thinking about each trial; rather, they spend more time thinking about the ``hard'' trials than the ``easy'' trials.

In addition, we found that response time is affected by the number of bounces during feedback; participants were slower to respond as more bounces were added. While this may be partially modulated by difficulty---people make more variable predictions as bounces are added \cite{Smith:2013fc}, and more variable trials have longer reaction times---there appears to be an additional time cost. \TODO{Can we add statistics here? E.g., how much additional time, and something showing that this is above and beyond difficulty (intercept differences with quadratic fits)?} This suggests that it takes additional time to resolve a collision between the ball and a wall in the course of a simulation. We will use this theory to further explain expected reaction times in \TODO{Add section here}.

\section{Modeling mental sampling}

How do people make the judgment that the ball will go through the hole? Following the success of SPRT, we hypothesized that they predict where the ball will go by running noisy physical simulations, and that they run a variable number of simulations on each trial based on SPRT principles \cite{wald1947sequential}. In this section, we lay out the formalism for the simulation-based sampling model, consisting of a physical simulator and SPRT sampler.

\subsection{The physical simulator}

There is a growing body of evidence that people reason about physical scenes by running noisy simulations. This hypothesis, referred to as the ``noisy Newton'' hypothesis, states that people have approximate knowledge of physical laws instantiated in a runnable model of intuitive physics. Using this model, they can extrapolate the future of physical scenes by running a series of noisy simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}. In particular, \citeA{Smith:2013fc} investigated the various sources of uncertainty in these simulations, finding that people's judgments were best captured by a model that took into account both perceptual uncertainty (noise in exactly where objects are and their motion trajectories) and dynamic uncertainty (stochastic noise added to account for unknowable variation in motion---e.g., a textured floor would cause a ball rolling along it to deviate from a straight line).

@@

Here, we used the model of \citeA{Smith:2013fc} to describe how people simulate individual possible physical events. Because the hole-choice experiment was performed online, we performed an online replication of that experiment to set model parameters (see the Appendix for details). Thus the physical prediction parameters were set independently of the performance on this experiment.

\subsection{The SPRT sampler}

The physical prediction model provides a posterior predictive distribution of where the ball will be when it encounters the plane of the wall. However, it is possible that the participants in the auxiliary experiment used more than one sample to determine where the ball would go. Assuming they took on average $M$ samples, then the standard deviation we are estimating using the physical simulator ($\sigma_{judgments}$) is not equal to the standard deviation of distributions of simulations ($\sigma_{sims}$), but is instead related by the equation: $\sigma_{sims} = \sigma_{judgments} / \sqrt{M}$. Therefore, we allowed for one free parameter to adjust this variance such that $\sigma_{adj}=\sqrt{M}$.

If sampling is pulling from this distribution, the probability of a ball going `in' ($H_1$) on any given sample is simply the density of the probability distribution that overlaps with the hole ($p$). So for a given threshold $T$, we can calculate the expected number of samples for any trial using equation \ref{eq:expsamp}.

\subsection{Modeling reaction time}

If we assume that every same takes the same amount of time, response times as predicted by the model should be directly proportional to $\mathbb{E}[N\,|\,T,p]$. However, we found the number of bounces to be an extremely strong predictor of response time: each additional bounce adds a constant amount of time to the response. To account for this, our final response time equation incorporated the number of bounces, $B$, as follows:
\begin{equation}
t = \beta_0 + (\beta_1 + \beta_2\cdot{}\mathbb{E}[B]) \cdot{}\mathbb{E}[N\,|\,T,p]
\label{eq:rt}
\end{equation}

We could use the physical simulation model to determine $\mathbb{E}[B]$ as the average number of times the ball bounced across all model simulations. We then fit all coefficients ($\beta_0$, $\beta_1$, and $\beta_2$, $\sigma_{adj}$, and $T$) to minimize sum squared error between modeled and observed reaction times.

The fitted model explained the data well, explaining both how accurate participants were for each trial (\HoleResponseCorr{}), and how quickly participants responded to trials (\HoleRTCorr{}, see Figure \ref{fig:model-results}).

\TODO{Can we show that accuracy correlation is better with SPRT softmaxing than strict accuracy to further suggest varying number of samples?}

In addition, the parameters of the sampling process can further inform us about how people accomplish physical prediction. The best fitting threshold was \threshold{}, suggesting people gather little information before making a decision (in line with the theory of \cite{Vul:2014ba}, see the Discussion). \TODO{KS ENDED EDITS HERE}

\section{Appendix: Experiment for setting physical model parameters}
